Efficient pedigree recording for fast population genetics simulation

### 2017-12-27 forwards_paper.tex
add missing word

Our approach to simplification is based on Hudson's algorithm for simulating
the coalescent with recombination~\citep{hudson1983properties},
paralleling the implementation in \msprime{} \citep{kelleher2016efficient};
an implementation in pseudocode is provided in Appendix~\ref{ss:simplify_algorithm}.
Conceptually, this works by
(a) beginning by painting the chromosome each sample a distinct color;
(b) moving back through history,
copying the colors of each chromosome to the portions of its' parental chromosomes
from which it was inherited;
(c) each time we would paint two colors in the same spot (a coalescence),
record that information as an edge and instead paint a brand-new color;
and
(d) once all colors have coalesced on a given segment,
stop propagating it.
This ``paint pot'' description misses some details --
for instance, we must ensure that all coalescing segments in a given individual
are assigned the \emph{same} new color --
but is reasonably close.
Figure~\ref{fig:method_diagram} shows an example tree sequence,
before and after simplification,
and Figure~\ref{fig:simplify_state} depicts the ``paint pot'' state of the algorithm
during the process of simplifying this tree sequence.

>>>>

Our approach to simplification is based on Hudson's algorithm for simulating
the coalescent with recombination~\citep{hudson1983properties},
paralleling the implementation in \msprime{} \citep{kelleher2016efficient};
an implementation in pseudocode is provided in Appendix~\ref{ss:simplify_algorithm}.
Conceptually, this works by
(a) beginning by painting the chromosome in each sample a distinct color;
(b) moving back through history,
copying the colors of each chromosome to the portions of its' parental chromosomes
from which it was inherited;
(c) each time we would paint two colors in the same spot (a coalescence),
record that information as an edge and instead paint a brand-new color;
and
(d) once all colors have coalesced on a given segment,
stop propagating it.
This ``paint pot'' description misses some details --
for instance, we must ensure that all coalescing segments in a given individual
are assigned the \emph{same} new color --
but is reasonably close.
Figure~\ref{fig:method_diagram} shows an example tree sequence,
before and after simplification,
and Figure~\ref{fig:simplify_state} depicts the ``paint pot'' state of the algorithm
during the process of simplifying this tree sequence.
